parental migration and adolescents educational performance

### 2023-03-24 data/Gu-thesis-script-more-control-var.Rmd

Control variables
```{r}
d_cl <- d_cl %>% mutate(
         is.girl = if_else(a01 == 2, 1, 0), #student is girl
         is.rural = if_else(bd05 == 1, 1, 0), #student holds rural (agricultural) hukou
         is.only.child = if_else(b01 == 1, 1, 0), #student is only child
         is.boarding = if_else(c18 == 1 & w2b15 == 1, 1, 0), #student is boarding at school at both baseline and endline
         siblings = if_else(b01 == 1, 0, b0201 + b0202 + b0203 + b0204),
         health = NA,
         par.edu = if_else(b06 > b07, b06, b07), #best educated parent
         fa.edu = b07,
         mo.edu = b06,
         home.internet = if_else(b13 == 2, 1, 0), #student has internet access at home
         home.book = NA #Amount of book at home, student self-rated 
)
```

@@

```{r}
d_cl$health[d_cl$a17==1 | d_cl$a17==2] <- 1
d_cl$health[d_cl$a17==3] <- 2
d_cl$health[d_cl$a17==4 | d_cl$a17==5] <- 3
```

@@

Regressing on cognitive test score (standardized)
```{r}
did_adj_cog <- feols(cog ~ migr  + age + is.girl + is.rural + siblings + health +is.boarding + par.edu.year + home.book + home.internet | schids, data = d_cl) 
did_adj_cog_m_only <- feols(cog ~ migr_mo_only   + age + is.girl + is.rural + siblings + health +is.boarding + par.edu.year + home.book + home.internet | schids, data = d_cl) 
did_adj_cog_m <- feols(cog ~ migr_mo   + age + is.girl + is.rural + siblings + health +is.boarding + par.edu.year + home.book + home.internet | schids, data = d_cl) 
did_adj_cog_f_only <- feols(cog ~ migr_fa_only   + age + is.girl + is.rural + siblings + health +is.boarding + par.edu.year + home.book + home.internet | schids, data = d_cl) 
did_adj_cog_f <- feols(cog ~ migr_fa   + age + is.girl + is.rural + siblings + health +is.boarding + par.edu.year + home.book + home.internet | schids, data = d_cl) 
did_adj_cog_both <- feols(cog ~ migr_both   + age + is.girl + is.rural + siblings + health +is.boarding + par.edu.year + home.book + home.internet | schids, data = d_cl)
```

@@

Regressing on total exam score
```{r}
did_adj_ttl <- feols(ttl_std ~ migr   + age + is.girl + is.rural + siblings + health +is.boarding + par.edu.year + home.book + home.internet | schids, data = d_cl) 
did_adj_ttl_m_only <- feols(ttl_std ~ migr_mo_only   + age + is.girl + is.rural + siblings + health +is.boarding + par.edu.year + home.book + home.internet | schids, data = d_cl) 
did_adj_ttl_m <- feols(ttl_std ~ migr_mo   + age + is.girl + is.rural + siblings + health +is.boarding + par.edu.year + home.book + home.internet | schids, data = d_cl) 
did_adj_ttl_f <- feols(ttl_std ~ migr_fa   + age + is.girl + is.rural + siblings + health +is.boarding + par.edu.year + home.book + home.internet | schids, data = d_cl) 
did_adj_ttl_f_only <- feols(ttl_std ~ migr_fa_only   + age + is.girl + is.rural + siblings + health +is.boarding + par.edu.year + home.book + home.internet | schids, data = d_cl) 
did_adj_ttl_both <- feols(ttl_std ~ migr_both   + age + is.girl + is.rural + siblings + health +is.boarding + par.edu.year + home.book + home.internet | schids, data = d_cl)
```

@@

Regressing on Chinese exam score
```{r}
did_adj_chn <- feols(chn_std ~ migr   + age + is.girl + is.rural + siblings + health +is.boarding + par.edu.year + home.book + home.internet | schids, data = d_cl) 
did_adj_chn_m_only <- feols(chn_std ~ migr_mo_only   + age + is.girl + is.rural + siblings + health +is.boarding + par.edu.year + home.book + home.internet | schids, data = d_cl) 
did_adj_chn_m <- feols(chn_std ~ migr_mo   + age + is.girl + is.rural + siblings + health +is.boarding + par.edu.year + home.book + home.internet | schids, data = d_cl) 
did_adj_chn_f_only <- feols(chn_std ~ migr_fa_only   + age + is.girl + is.rural + siblings + health +is.boarding + par.edu.year + home.book + home.internet | schids, data = d_cl) 
did_adj_chn_f <- feols(chn_std ~ migr_fa   + age + is.girl + is.rural + siblings + health +is.boarding + par.edu.year + home.book + home.internet | schids, data = d_cl) 
did_adj_chn_both <- feols(chn_std ~ migr_both   + age + is.girl + is.rural + siblings + health +is.boarding + par.edu.year + home.book + home.internet | schids, data = d_cl)
```

@@

Regressing on Math score
```{r}
did_adj_mat <- feols(mat_std ~ migr   + age + is.girl + is.rural + siblings + health +is.boarding + par.edu.year + home.book + home.internet | schids, data = d_cl) 
did_adj_mat_m_only <- feols(mat_std ~ migr_mo_only   + age + is.girl + is.rural + siblings + health +is.boarding + par.edu.year + home.book + home.internet | schids, data = d_cl) 
did_adj_mat_m <- feols(mat_std ~ migr_mo   + age + is.girl + is.rural + siblings + health +is.boarding + par.edu.year + home.book + home.internet | schids, data = d_cl) 
did_adj_mat_f_only <- feols(mat_std ~ migr_fa_only   + age + is.girl + is.rural + siblings + health +is.boarding + par.edu.year + home.book + home.internet | schids, data = d_cl) 
did_adj_mat_f <- feols(mat_std ~ migr_fa   + age + is.girl + is.rural + siblings + health +is.boarding + par.edu.year + home.book + home.internet | schids, data = d_cl) 
did_adj_mat_both <- feols(mat_std ~ migr_both   + age + is.girl + is.rural + siblings + health +is.boarding + par.edu.year + home.book + home.internet | schids, data = d_cl)
```

@@

Regressing on English score
```{r}
did_adj_eng <- feols(eng_std ~ migr  + age + is.girl + is.rural + siblings + health +is.boarding + par.edu.year + home.book + home.internet | schids, data = d_cl) 
did_adj_eng_m <- feols(eng_std ~ migr_mo  + age + is.girl + is.rural + siblings + health +is.boarding + par.edu.year + home.book + home.internet | schids, data = d_cl)
did_adj_eng_m_only <- feols(eng_std ~ migr_mo_only  + age + is.girl + is.rural + siblings + health +is.boarding + par.edu.year + home.book + home.internet | schids, data = d_cl) 
did_adj_eng_f <- feols(eng_std ~ migr_fa  + age + is.girl + is.rural + siblings + health +is.boarding + par.edu.year + home.book + home.internet | schids, data = d_cl) 
did_adj_eng_f_only <- feols(eng_std ~ migr_fa_only  + age + is.girl + is.rural + siblings + health +is.boarding + par.edu.year + home.book + home.internet | schids, data = d_cl) 
did_adj_eng_both <- feols(eng_std ~ migr_both  + age + is.girl + is.rural + siblings + health +is.boarding + par.edu.year + home.book + home.internet | schids, data = d_cl)
```

@@

Regressing on cognitive test score (standardized)
```{r}
did_adj_unres_cog <- feols(cog ~ migr + cog3pl  + age + is.girl + is.rural + siblings + health +is.boarding + par.edu.year + home.book + home.internet | schids, data = d_cl) 
did_adj_unres_cog_m_only <- feols(cog ~ migr_mo_only + cog3pl  + age + is.girl + is.rural + siblings + health +is.boarding + par.edu.year + home.book + home.internet | schids, data = d_cl) 
did_adj_unres_cog_m <- feols(cog ~ migr_mo + cog3pl  + age + is.girl + is.rural + siblings + health +is.boarding + par.edu.year + home.book + home.internet | schids, data = d_cl) 
did_adj_unres_cog_f_only <- feols(cog ~ migr_fa_only + cog3pl  + age + is.girl + is.rural + siblings + health +is.boarding + par.edu.year + home.book + home.internet | schids, data = d_cl) 
did_adj_unres_cog_f <- feols(cog ~ migr_fa + cog3pl  + age + is.girl + is.rural + siblings + health +is.boarding + par.edu.year + home.book + home.internet | schids, data = d_cl) 
did_adj_unres_cog_both <- feols(cog ~ migr_both + cog3pl  + age + is.girl + is.rural + siblings + health +is.boarding + par.edu.year + home.book + home.internet | schids, data = d_cl)
```
Results
```{r}
models_adj_unres_cog <- list(
did_adj_unres_cog,
did_adj_unres_cog_m_only,
did_adj_unres_cog_m,
did_adj_unres_cog_f,
did_adj_unres_cog_f_only,
did_adj_unres_cog_both) 
models_adj_unres_cog %>% msummary(stars = c('*' = .05, '**' = .01, '***' = .001))
```
Regressing on total exam score
```{r}
did_adj_unres_ttl <- feols(ttl_std ~ migr + w1ttl_std  + age + is.girl + is.rural + siblings + health +is.boarding + par.edu.year + home.book + home.internet | schids, data = d_cl) 
did_adj_unres_ttl_m_only <- feols(ttl_std ~ migr_mo_only + w1ttl_std  + age + is.girl + is.rural + siblings + health +is.boarding + par.edu.year + home.book + home.internet | schids, data = d_cl) 
did_adj_unres_ttl_m <- feols(ttl_std ~ migr_mo + w1ttl_std  + age + is.girl + is.rural + siblings + health +is.boarding + par.edu.year + home.book + home.internet | schids, data = d_cl) 
did_adj_unres_ttl_f <- feols(ttl_std ~ migr_fa + w1ttl_std  + age + is.girl + is.rural + siblings + health +is.boarding + par.edu.year + home.book + home.internet | schids, data = d_cl) 
did_adj_unres_ttl_f_only <- feols(ttl_std ~ migr_fa_only + w1ttl_std  + age + is.girl + is.rural + siblings + health +is.boarding + par.edu.year + home.book + home.internet | schids, data = d_cl) 
did_adj_unres_ttl_both <- feols(ttl_std ~ migr_both + w1ttl_std  + age + is.girl + is.rural + siblings + health +is.boarding + par.edu.year + home.book + home.internet | schids, data = d_cl)
```
Results
```{r}
models_adj_unres_ttl <- list(
did_adj_unres_ttl,
did_adj_unres_ttl_m_only,
did_adj_unres_ttl_m,
did_adj_unres_ttl_f,
did_adj_unres_ttl_f_only,
did_adj_unres_ttl_both) 
models_adj_unres_ttl %>% msummary(stars = c('*' = .05, '**' = .01, '***' = .001))
```

Regressing on Chinese exam score
```{r}
did_adj_unres_chn <- feols(chn_std ~ migr + w1chn_std  + age + is.girl + is.rural + siblings + health +is.boarding + par.edu.year + home.book + home.internet | schids, data = d_cl) 
did_adj_unres_chn_m_only <- feols(chn_std ~ migr_mo_only + w1chn_std  + age + is.girl + is.rural + siblings + health +is.boarding + par.edu.year + home.book + home.internet | schids, data = d_cl) 
did_adj_unres_chn_m <- feols(chn_std ~ migr_mo + w1chn_std  + age + is.girl + is.rural + siblings + health +is.boarding + par.edu.year + home.book + home.internet | schids, data = d_cl) 
did_adj_unres_chn_f_only <- feols(chn_std ~ migr_fa_only + w1chn_std  + age + is.girl + is.rural + siblings + health +is.boarding + par.edu.year + home.book + home.internet | schids, data = d_cl) 
did_adj_unres_chn_f <- feols(chn_std ~ migr_fa + w1chn_std  + age + is.girl + is.rural + siblings + health +is.boarding + par.edu.year + home.book + home.internet | schids, data = d_cl) 
did_adj_unres_chn_both <- feols(chn_std ~ migr_both + w1chn_std  + age + is.girl + is.rural + siblings + health +is.boarding + par.edu.year + home.book + home.internet | schids, data = d_cl)
```
Results
```{r}
models_adj_unres_chn <- list(
did_adj_unres_chn,
did_adj_unres_chn_m_only,
did_adj_unres_chn_m,
did_adj_unres_chn_f,
did_adj_unres_chn_f_only,
did_adj_unres_chn_both) 
models_adj_unres_chn %>% msummary(stars = c('*' = .05, '**' = .01, '***' = .001))
```

Regressing on Math score
```{r}
did_adj_unres_mat <- feols(mat_std ~ migr + w1mat_std  + age + is.girl + is.rural + siblings + health +is.boarding + par.edu.year + home.book + home.internet | schids, data = d_cl) 
did_adj_unres_mat_m_only <- feols(mat_std ~ migr_mo_only + w1mat_std  + age + is.girl + is.rural + siblings + health +is.boarding + par.edu.year + home.book + home.internet | schids, data = d_cl) 
did_adj_unres_mat_m <- feols(mat_std ~ migr_mo + w1mat_std  + age + is.girl + is.rural + siblings + health +is.boarding + par.edu.year + home.book + home.internet | schids, data = d_cl) 
did_adj_unres_mat_f_only <- feols(mat_std ~ migr_fa_only + w1mat_std  + age + is.girl + is.rural + siblings + health +is.boarding + par.edu.year + home.book + home.internet | schids, data = d_cl) 
did_adj_unres_mat_f <- feols(mat_std ~ migr_fa + w1mat_std  + age + is.girl + is.rural + siblings + health +is.boarding + par.edu.year + home.book + home.internet | schids, data = d_cl) 
did_adj_unres_mat_both <- feols(mat_std ~ migr_both + w1mat_std  + age + is.girl + is.rural + siblings + health +is.boarding + par.edu.year + home.book + home.internet | schids, data = d_cl)
```
Results
```{r}
models_mat_adj_unres <- list(
did_adj_unres_mat,
did_adj_unres_mat_m_only,
did_adj_unres_mat_m,
did_adj_unres_mat_f,
did_adj_unres_mat_f_only,
did_adj_unres_mat_both) 
models_mat_adj_unres %>% msummary(stars = c('*' = .05, '**' = .01, '***' = .001))
```

Regressing on English score
```{r}
did_adj_unres_eng <- feols(eng_std ~ migr + w1eng_std  + age + is.girl + is.rural + siblings + health +is.boarding + par.edu.year + home.book + home.internet | schids, data = d_cl) 
did_adj_unres_eng_m <- feols(eng_std ~ migr_mo + w1eng_std  + age + is.girl + is.rural + siblings + health +is.boarding + par.edu.year + home.book + home.internet | schids, data = d_cl)
did_adj_unres_eng_m_only <- feols(eng_std ~ migr_mo_only + w1eng_std  + age + is.girl + is.rural + siblings + health +is.boarding + par.edu.year + home.book + home.internet | schids, data = d_cl) 
did_adj_unres_eng_f <- feols(eng_std ~ migr_fa + w1eng_std  + age + is.girl + is.rural + siblings + health +is.boarding + par.edu.year + home.book + home.internet | schids, data = d_cl) 
did_adj_unres_eng_f_only <- feols(eng_std ~ migr_fa_only + w1eng_std  + age + is.girl + is.rural + siblings + health +is.boarding + par.edu.year + home.book + home.internet | schids, data = d_cl) 
did_adj_unres_eng_both <- feols(eng_std ~ migr_both + w1eng_std  + age + is.girl + is.rural + siblings + health +is.boarding + par.edu.year + home.book + home.internet | schids, data = d_cl)
```
Results
```{r}
models_adj_unres_eng <- list(
did_adj_unres_eng,
did_adj_unres_eng_m_only,
did_adj_unres_eng_m,
did_adj_unres_eng_f,
did_adj_unres_eng_f_only,
did_adj_unres_eng_both) 
models_adj_unres_eng %>% msummary(stars = c('*' = .05, '**' = .01, '***' = .001))
```

>>>>

Control variables
```{r}
d_cl <- d_cl %>% mutate(
         is.girl = if_else(a01 == 2, 1, 0), #student is girl
         is.rural = if_else(bd05 == 1, 1, 0), #student holds rural (agricultural) hukou
         is.only.child = if_else(b01 == 1, 1, 0), #student is only child
         is.boarding = if_else(c18 == 1 & w2b15 == 1, 1, 0), #student is boarding at school at both baseline and endline
         ch.siblings = if_else(b01 == 1, 0, b0201 + b0202 + b0203 + b0204),
         ch.health = NA,
         ch.edu.aspr = NA,
         par.edu = if_else(b06 > b07, b06, b07), #best educated parent
         fa.edu = b07,
         mo.edu = b06,
         home.internet = if_else(b13 == 2, 1, 0), #student has internet access at home
         home.book = NA #Amount of book at home, student self-rated 
)
```

@@

```{r}
d_cl$ch.health[d_cl$a17==1 | d_cl$a17==2] <- 1
d_cl$ch.health[d_cl$a17==3] <- 2
d_cl$ch.health[d_cl$a17==4 | d_cl$a17==5] <- 3
```

```{r}
d_cl$ch.edu.aspr[d_cl$c22==10] <- 0
d_cl$ch.edu.aspr[d_cl$c22==1 | d_cl$c22==2] <- 1
d_cl$ch.edu.aspr[d_cl$c22==3 | d_cl$c22==4 | d_cl$c22==5] <- 2
d_cl$ch.edu.aspr[d_cl$c22==6 | d_cl$c22==7] <- 3
d_cl$ch.edu.aspr[d_cl$c22==8 | d_cl$c22==9] <- 4
```

@@

Regressing on cognitive test score (standardized)
```{r}
did_adj_cog <- feols(cog ~ migr  + age + is.girl + is.rural + ch.siblings + health +is.boarding + par.edu.year + home.book + home.internet | schids, data = d_cl) 
did_adj_cog_m_only <- feols(cog ~ migr_mo_only   + age + is.girl + is.rural + ch.siblings + health +is.boarding + par.edu.year + home.book + home.internet | schids, data = d_cl) 
did_adj_cog_m <- feols(cog ~ migr_mo   + age + is.girl + is.rural + ch.siblings + health +is.boarding + par.edu.year + home.book + home.internet | schids, data = d_cl) 
did_adj_cog_f_only <- feols(cog ~ migr_fa_only   + age + is.girl + is.rural + ch.siblings + health +is.boarding + par.edu.year + home.book + home.internet | schids, data = d_cl) 
did_adj_cog_f <- feols(cog ~ migr_fa   + age + is.girl + is.rural + ch.siblings + health +is.boarding + par.edu.year + home.book + home.internet | schids, data = d_cl) 
did_adj_cog_both <- feols(cog ~ migr_both   + age + is.girl + is.rural + ch.siblings + health +is.boarding + par.edu.year + home.book + home.internet | schids, data = d_cl)
```

@@

Regressing on total exam score
```{r}
did_adj_ttl <- feols(ttl_std ~ migr   + age + is.girl + is.rural + ch.siblings + health +is.boarding + par.edu.year + home.book + home.internet | schids, data = d_cl) 
did_adj_ttl_m_only <- feols(ttl_std ~ migr_mo_only   + age + is.girl + is.rural + ch.siblings + health +is.boarding + par.edu.year + home.book + home.internet | schids, data = d_cl) 
did_adj_ttl_m <- feols(ttl_std ~ migr_mo   + age + is.girl + is.rural + ch.siblings + health +is.boarding + par.edu.year + home.book + home.internet | schids, data = d_cl) 
did_adj_ttl_f <- feols(ttl_std ~ migr_fa   + age + is.girl + is.rural + ch.siblings + health +is.boarding + par.edu.year + home.book + home.internet | schids, data = d_cl) 
did_adj_ttl_f_only <- feols(ttl_std ~ migr_fa_only   + age + is.girl + is.rural + ch.siblings + health +is.boarding + par.edu.year + home.book + home.internet | schids, data = d_cl) 
did_adj_ttl_both <- feols(ttl_std ~ migr_both   + age + is.girl + is.rural + ch.siblings + health +is.boarding + par.edu.year + home.book + home.internet | schids, data = d_cl)
```

@@

Regressing on Chinese exam score
```{r}
did_adj_chn <- feols(chn_std ~ migr   + age + is.girl + is.rural + ch.siblings + health +is.boarding + par.edu.year + home.book + home.internet | schids, data = d_cl) 
did_adj_chn_m_only <- feols(chn_std ~ migr_mo_only   + age + is.girl + is.rural + ch.siblings + health +is.boarding + par.edu.year + home.book + home.internet | schids, data = d_cl) 
did_adj_chn_m <- feols(chn_std ~ migr_mo   + age + is.girl + is.rural + ch.siblings + health +is.boarding + par.edu.year + home.book + home.internet | schids, data = d_cl) 
did_adj_chn_f_only <- feols(chn_std ~ migr_fa_only   + age + is.girl + is.rural + ch.siblings + health +is.boarding + par.edu.year + home.book + home.internet | schids, data = d_cl) 
did_adj_chn_f <- feols(chn_std ~ migr_fa   + age + is.girl + is.rural + ch.siblings + health +is.boarding + par.edu.year + home.book + home.internet | schids, data = d_cl) 
did_adj_chn_both <- feols(chn_std ~ migr_both   + age + is.girl + is.rural + ch.siblings + health +is.boarding + par.edu.year + home.book + home.internet | schids, data = d_cl)
```

@@

Regressing on Math score
```{r}
did_adj_mat <- feols(mat_std ~ migr   + age + is.girl + is.rural + ch.siblings + health +is.boarding + par.edu.year + home.book + home.internet | schids, data = d_cl) 
did_adj_mat_m_only <- feols(mat_std ~ migr_mo_only   + age + is.girl + is.rural + ch.siblings + health +is.boarding + par.edu.year + home.book + home.internet | schids, data = d_cl) 
did_adj_mat_m <- feols(mat_std ~ migr_mo   + age + is.girl + is.rural + ch.siblings + health +is.boarding + par.edu.year + home.book + home.internet | schids, data = d_cl) 
did_adj_mat_f_only <- feols(mat_std ~ migr_fa_only   + age + is.girl + is.rural + ch.siblings + health +is.boarding + par.edu.year + home.book + home.internet | schids, data = d_cl) 
did_adj_mat_f <- feols(mat_std ~ migr_fa   + age + is.girl + is.rural + ch.siblings + health +is.boarding + par.edu.year + home.book + home.internet | schids, data = d_cl) 
did_adj_mat_both <- feols(mat_std ~ migr_both   + age + is.girl + is.rural + ch.siblings + health +is.boarding + par.edu.year + home.book + home.internet | schids, data = d_cl)
```

@@

Regressing on English score
```{r}
did_adj_eng <- feols(eng_std ~ migr  + age + is.girl + is.rural + ch.siblings + health +is.boarding + par.edu.year + home.book + home.internet | schids, data = d_cl) 
did_adj_eng_m <- feols(eng_std ~ migr_mo  + age + is.girl + is.rural + ch.siblings + health +is.boarding + par.edu.year + home.book + home.internet | schids, data = d_cl)
did_adj_eng_m_only <- feols(eng_std ~ migr_mo_only  + age + is.girl + is.rural + ch.siblings + health +is.boarding + par.edu.year + home.book + home.internet | schids, data = d_cl) 
did_adj_eng_f <- feols(eng_std ~ migr_fa  + age + is.girl + is.rural + ch.siblings + health +is.boarding + par.edu.year + home.book + home.internet | schids, data = d_cl) 
did_adj_eng_f_only <- feols(eng_std ~ migr_fa_only  + age + is.girl + is.rural + ch.siblings + health +is.boarding + par.edu.year + home.book + home.internet | schids, data = d_cl) 
did_adj_eng_both <- feols(eng_std ~ migr_both  + age + is.girl + is.rural + ch.siblings + health +is.boarding + par.edu.year + home.book + home.internet | schids, data = d_cl)
```

@@

Regressing on cognitive test score (standardized)
```{r}
did_adj_unres_cog <- feols(cog ~ migr + cog3pl  + age + is.girl + is.rural + ch.siblings + health +is.boarding + par.edu.year + home.book + home.internet | schids, data = d_cl) 
did_adj_unres_cog_m_only <- feols(cog ~ migr_mo_only + cog3pl  + age + is.girl + is.rural + ch.siblings + health +is.boarding + par.edu.year + home.book + home.internet | schids, data = d_cl) 
did_adj_unres_cog_m <- feols(cog ~ migr_mo + cog3pl  + age + is.girl + is.rural + ch.siblings + health +is.boarding + par.edu.year + home.book + home.internet | schids, data = d_cl) 
did_adj_unres_cog_f_only <- feols(cog ~ migr_fa_only + cog3pl  + age + is.girl + is.rural + ch.siblings + health +is.boarding + par.edu.year + home.book + home.internet | schids, data = d_cl) 
did_adj_unres_cog_f <- feols(cog ~ migr_fa + cog3pl  + age + is.girl + is.rural + ch.siblings + health +is.boarding + par.edu.year + home.book + home.internet | schids, data = d_cl) 
did_adj_unres_cog_both <- feols(cog ~ migr_both + cog3pl  + age + is.girl + is.rural + ch.siblings + health +is.boarding + par.edu.year + home.book + home.internet | schids, data = d_cl)
```
Results
```{r}
models_adj_unres_cog <- list(
did_adj_unres_cog,
did_adj_unres_cog_m_only,
did_adj_unres_cog_m,
did_adj_unres_cog_f,
did_adj_unres_cog_f_only,
did_adj_unres_cog_both) 
models_adj_unres_cog %>% msummary(stars = c('*' = .05, '**' = .01, '***' = .001))
```
Regressing on total exam score
```{r}
did_adj_unres_ttl <- feols(ttl_std ~ migr + w1ttl_std  + age + is.girl + is.rural + ch.siblings + health +is.boarding + par.edu.year + home.book + home.internet | schids, data = d_cl) 
did_adj_unres_ttl_m_only <- feols(ttl_std ~ migr_mo_only + w1ttl_std  + age + is.girl + is.rural + ch.siblings + health +is.boarding + par.edu.year + home.book + home.internet | schids, data = d_cl) 
did_adj_unres_ttl_m <- feols(ttl_std ~ migr_mo + w1ttl_std  + age + is.girl + is.rural + ch.siblings + health +is.boarding + par.edu.year + home.book + home.internet | schids, data = d_cl) 
did_adj_unres_ttl_f <- feols(ttl_std ~ migr_fa + w1ttl_std  + age + is.girl + is.rural + ch.siblings + health +is.boarding + par.edu.year + home.book + home.internet | schids, data = d_cl) 
did_adj_unres_ttl_f_only <- feols(ttl_std ~ migr_fa_only + w1ttl_std  + age + is.girl + is.rural + ch.siblings + health +is.boarding + par.edu.year + home.book + home.internet | schids, data = d_cl) 
did_adj_unres_ttl_both <- feols(ttl_std ~ migr_both + w1ttl_std  + age + is.girl + is.rural + ch.siblings + health +is.boarding + par.edu.year + home.book + home.internet | schids, data = d_cl)
```
Results
```{r}
models_adj_unres_ttl <- list(
did_adj_unres_ttl,
did_adj_unres_ttl_m_only,
did_adj_unres_ttl_m,
did_adj_unres_ttl_f,
did_adj_unres_ttl_f_only,
did_adj_unres_ttl_both) 
models_adj_unres_ttl %>% msummary(stars = c('*' = .05, '**' = .01, '***' = .001))
```

Regressing on Chinese exam score
```{r}
did_adj_unres_chn <- feols(chn_std ~ migr + w1chn_std  + age + is.girl + is.rural + ch.siblings + health +is.boarding + par.edu.year + home.book + home.internet | schids, data = d_cl) 
did_adj_unres_chn_m_only <- feols(chn_std ~ migr_mo_only + w1chn_std  + age + is.girl + is.rural + ch.siblings + health +is.boarding + par.edu.year + home.book + home.internet | schids, data = d_cl) 
did_adj_unres_chn_m <- feols(chn_std ~ migr_mo + w1chn_std  + age + is.girl + is.rural + ch.siblings + health +is.boarding + par.edu.year + home.book + home.internet | schids, data = d_cl) 
did_adj_unres_chn_f_only <- feols(chn_std ~ migr_fa_only + w1chn_std  + age + is.girl + is.rural + ch.siblings + health +is.boarding + par.edu.year + home.book + home.internet | schids, data = d_cl) 
did_adj_unres_chn_f <- feols(chn_std ~ migr_fa + w1chn_std  + age + is.girl + is.rural + ch.siblings + health +is.boarding + par.edu.year + home.book + home.internet | schids, data = d_cl) 
did_adj_unres_chn_both <- feols(chn_std ~ migr_both + w1chn_std  + age + is.girl + is.rural + ch.siblings + health +is.boarding + par.edu.year + home.book + home.internet | schids, data = d_cl)
```
Results
```{r}
models_adj_unres_chn <- list(
did_adj_unres_chn,
did_adj_unres_chn_m_only,
did_adj_unres_chn_m,
did_adj_unres_chn_f,
did_adj_unres_chn_f_only,
did_adj_unres_chn_both) 
models_adj_unres_chn %>% msummary(stars = c('*' = .05, '**' = .01, '***' = .001))
```

Regressing on Math score
```{r}
did_adj_unres_mat <- feols(mat_std ~ migr + w1mat_std  + age + is.girl + is.rural + ch.siblings + health +is.boarding + par.edu.year + home.book + home.internet | schids, data = d_cl) 
did_adj_unres_mat_m_only <- feols(mat_std ~ migr_mo_only + w1mat_std  + age + is.girl + is.rural + ch.siblings + health +is.boarding + par.edu.year + home.book + home.internet | schids, data = d_cl) 
did_adj_unres_mat_m <- feols(mat_std ~ migr_mo + w1mat_std  + age + is.girl + is.rural + ch.siblings + health +is.boarding + par.edu.year + home.book + home.internet | schids, data = d_cl) 
did_adj_unres_mat_f_only <- feols(mat_std ~ migr_fa_only + w1mat_std  + age + is.girl + is.rural + ch.siblings + health +is.boarding + par.edu.year + home.book + home.internet | schids, data = d_cl) 
did_adj_unres_mat_f <- feols(mat_std ~ migr_fa + w1mat_std  + age + is.girl + is.rural + ch.siblings + health +is.boarding + par.edu.year + home.book + home.internet | schids, data = d_cl) 
did_adj_unres_mat_both <- feols(mat_std ~ migr_both + w1mat_std  + age + is.girl + is.rural + ch.siblings + health +is.boarding + par.edu.year + home.book + home.internet | schids, data = d_cl)
```
Results
```{r}
models_mat_adj_unres <- list(
did_adj_unres_mat,
did_adj_unres_mat_m_only,
did_adj_unres_mat_m,
did_adj_unres_mat_f,
did_adj_unres_mat_f_only,
did_adj_unres_mat_both) 
models_mat_adj_unres %>% msummary(stars = c('*' = .05, '**' = .01, '***' = .001))
```

Regressing on English score
```{r}
did_adj_unres_eng <- feols(eng_std ~ migr + w1eng_std  + age + is.girl + is.rural + ch.siblings + health +is.boarding + par.edu.year + home.book + home.internet | schids, data = d_cl) 
did_adj_unres_eng_m <- feols(eng_std ~ migr_mo + w1eng_std  + age + is.girl + is.rural + ch.siblings + health +is.boarding + par.edu.year + home.book + home.internet | schids, data = d_cl)
did_adj_unres_eng_m_only <- feols(eng_std ~ migr_mo_only + w1eng_std  + age + is.girl + is.rural + ch.siblings + health +is.boarding + par.edu.year + home.book + home.internet | schids, data = d_cl) 
did_adj_unres_eng_f <- feols(eng_std ~ migr_fa + w1eng_std  + age + is.girl + is.rural + ch.siblings + health +is.boarding + par.edu.year + home.book + home.internet | schids, data = d_cl) 
did_adj_unres_eng_f_only <- feols(eng_std ~ migr_fa_only + w1eng_std  + age + is.girl + is.rural + ch.siblings + health +is.boarding + par.edu.year + home.book + home.internet | schids, data = d_cl) 
did_adj_unres_eng_both <- feols(eng_std ~ migr_both + w1eng_std  + age + is.girl + is.rural + ch.siblings + health +is.boarding + par.edu.year + home.book + home.internet | schids, data = d_cl)
```
Results
```{r}
models_adj_unres_eng <- list(
did_adj_unres_eng,
did_adj_unres_eng_m_only,
did_adj_unres_eng_m,
did_adj_unres_eng_f,
did_adj_unres_eng_f_only,
did_adj_unres_eng_both) 
models_adj_unres_eng %>% msummary(stars = c('*' = .05, '**' = .01, '***' = .001))
```
